\bf Comparing the Power of Plot Designs to Reveal Correlation

### 2016-01-11 paper/paper.Rnw
tweaks

\begin{table}[htp]
\caption{Weighted Mixed Effects Logit Model for the predicted power of plot design. Sample size for scatter plot evaluations: 900, overlaid lines: 949, total: 1849. Default plot design is overlaid lines. The model is fitted using the GLIMMIX procedure in SAS.}
\label{tab1}
\centering
<<powerfit, dependson='setup', results='asis', echo=FALSE, message=FALSE, error=FALSE, warning=FALSE>>=
sasdata <- select(full.sub, rabs, n, alpha, rsgn, smoothed, design, subj_id, weights, correct, log_time)
sasdata$rabs <- as.numeric(sasdata$rabs)
sasdata$subj_id <- as.numeric(sasdata$subj_id)
sasadata <- mutate(sasdata, design = ifelse(design=="Scatterplot", 1, 0))
#write.csv(subsetted, "sas/choices.csv", row.names = FALSE)
powercoef <- powercoef[,-1]
rownames(powercoef) <- c("Intercept", "abs(r)", "sign(r)", "abs(r)*sign(r)", "smoothed", "t", "plot", "plot*abs(r)", "plot*sign(r)", "plot*abs(r)*sign(r)", "plot*smoothed", "plot*t")
colnames(powercoef) <- c("Estimate", "standard error", "df", "t-value", "p-value")
kable(powercoef, format="latex", digits=2)
@
\end{table}

Table \ref{tab1} summarises the model estimates. It can be confusing the interpret the model estimates, and at first glance it appears the negative plot coefficient implies that overliad lines are substantially more powerful than the scatter plot, but this is misleading and interpreting the full model involves combining the estimates for the different interactions with $abs(\rho)$ and $sign(\rho)$. $abs(\rho)$ models the power difference between low and high correlations, and $abs(\rho)*sign(\rho)$ models an increase in power appearing in positive but not negative correlation. 
Taking these into account, the scatter plot shows superior performance and higher values of abs($\rho$), It needs to be restated that we only tested correlations at  $0.3, 0.5, 0.7$ and $0.9$, so the results below an absolute value of $0.3$ are unreliable and may be artifacts of regression smoothing methods.

>>>>

\begin{table}[htp]
\caption{Weighted Mixed Effects Logit Model for the predicted power of plot design. Sample size for scatter plot evaluations: 900, overlaid lines: 949, total: 1849. Default plot design is overlaid lines. The model is fitted using the GLIMMIX procedure in SAS.}
\label{tab1}
\centering
<<powerfit, dependson='setup', results='asis', echo=FALSE, message=FALSE, error=FALSE, warning=FALSE>>=
sasdata <- select(full.sub, rabs, n, alpha, rsgn, smoothed, design, subj_id, weights, correct, log_time)
sasdata$rabs <- as.numeric(sasdata$rabs)
sasdata$subj_id <- as.numeric(sasdata$subj_id)
sasadata <- mutate(sasdata, design = ifelse(design=="Scatterplot", 1, 0))
#write.csv(subsetted, "sas/choices.csv", row.names = FALSE)
powercoef <- powercoef[,-1]
rownames(powercoef) <- c("Intercept", "abs(r)", "sign(r)", "abs(r)*sign(r)", "smoothed", "t", "design", "design*abs(r)", "design*sign(r)", "design*abs(r)*sign(r)", "design*smoothed", "design*t")
colnames(powercoef) <- c("Estimate", "standard error", "df", "t-value", "p-value")
kable(powercoef, format="latex", digits=2)
@
\end{table}

Table \ref{tab1} summarises the model estimates. It can be confusing the interpret the model estimates, and at first glance it appears the negative plot coefficient implies that overlaid lines are substantially more powerful than the scatter plot, but this is misleading and interpreting the full model involves combining the estimates for the different interactions with $\rho$. $\beta_{2}$ and $\beta_{8}$ model the power difference between low and high correlations, while $\beta_{3}, \beta_{4}, beta_{9}$ and $\beta_{10}$ model any increase in power appearing only in positive correlation. 
Taking these into account, the scatter plot shows superior performance relative to the overlaid lines at higher values of abs($\rho$). It needs to be restated that we only tested correlations at  $0.3, 0.5, 0.7$ and $0.9$, so the results below an absolute value of $0.3$ are unreliable and may be artifacts of regression smoothing methods.
